### 2015-12-07 mirror-descent.tex
Add references to Mirror Descent section

\textsc{Mirror Descent} is a generic algorithm similar to \textsc{Follow The
Regularized Leader} but quite different in details. The algorithm is stated as
Algorithm~\ref{algorithm:mirror-descent-varying-regularizer}. The algorithm is
parametrized by a sequence $\{R_t\}_{t=0}^\infty$ of convex functions $R_t:K
\to \R$ called \emph{regularizers}. Each regularizer $R_t$ can depend on past
loss vectors $\ell_1, \ell_2, \dots, \ell_t$ in an arbitrary way. If $R_t$ is
not differentiable\footnote{Note that this can happen even when $R_t$ is a
restriction of a differentiable function defined on a superset of $K$.  If $K$
is bounded and closed, $R_t$ fails to be differentiable at the boundary of $K$.
If $K$ is a subset of an affine subspace of a dimension smaller than the
dimension of $V$, then $R_t$ fails to be differentiable everywhere.}, Bregman
divergence, $\Breg_{R_t}(u,v) = R(u) - R(v) - \langle \grad R(v), u - v
\rangle$ needs to be defined. This is done by choosing a subgradient map $\grad
R_t:K \to V$, i.e. a function such that $\grad R_t(w)$ is a subgradient of
$R_t$ at a point $w$. If $R_t$ is a restriction of a differentiable function
$R'_t$, it is convenient to define $\grad R_t(w) = \grad R'_t(w)$ for all $w
\in K$. The following lemma bounds regret of \textsc{Mirror Descent}.  Proof
can be found in~\ref{section:mirror-descent-proofs}.

@@

Replacing $\frac{1}{2}\|w\|_2^2$ in equation \eqref{equation:ada-grad-regularizer} with
an arbitrary convex function $R:K \to \R$ yields
\begin{equation}
\label{equation:scale-free-mirror-descent}
R_t(w) = R(w) \sqrt{\sum_{i=1}^t \|\ell_i\|_*^2} \; .
\end{equation}
We call the resulting algorithm \textsc{Scale-Free Mirror Descent} with
regularizer $R$.  Generalizing existing regret bound for
\textsc{AdaGrad}~\cite{Duchi-Hazan-Singer-2011} we can upper bound its regret.
Proof can be found in~\ref{section:mirror-descent-proofs}.

>>>>

\textsc{Mirror Descent} is a generic algorithm similar to \textsc{Follow The
Regularized Leader} but quite different in details. The algorithm is stated as
Algorithm~\ref{algorithm:mirror-descent-varying-regularizer}. The algorithm is
parametrized by a sequence $\{R_t\}_{t=0}^\infty$ of convex functions $R_t:K
\to \R$ called \emph{regularizers}. Each regularizer $R_t$ can depend on past
loss vectors $\ell_1, \ell_2, \dots, \ell_t$ in an arbitrary way. If $R_t$ is
not differentiable\footnote{Note that this can happen even when $R_t$ is a
restriction of a differentiable function defined on a superset of $K$.  If $K$
is bounded and closed, $R_t$ fails to be differentiable at the boundary of $K$.
If $K$ is a subset of an affine subspace of a dimension smaller than the
dimension of $V$, then $R_t$ fails to be differentiable everywhere.}, Bregman
divergence, $\Breg_{R_t}(u,v) = R(u) - R(v) - \langle \grad R(v), u - v
\rangle$ needs to be defined. This is done by choosing a subgradient map $\grad
R_t:K \to V$, i.e. a function such that $\grad R_t(w)$ is a subgradient of
$R_t$ at a point $w$. If $R_t$ is a restriction of a differentiable function
$R'_t$, it is convenient to define $\grad R_t(w) = \grad R'_t(w)$ for all $w
\in K$. The following lemma bounds regret of \textsc{Mirror Descent}.  Proof
can be found in~\cite{Rakhlin-Sridharan-2009,Duchi-Shalev-Shwartz-Singer-Tewari-2010}.
For completeness we give a proof in~\ref{section:mirror-descent-proofs}.

@@

Replacing $\frac{1}{2}\|w\|_2^2$ in equation \eqref{equation:ada-grad-regularizer} with
an arbitrary convex function $R:K \to \R$ yields
\begin{equation}
\label{equation:scale-free-mirror-descent}
R_t(w) = R(w) \sqrt{\sum_{i=1}^t \|\ell_i\|_*^2} \; .
\end{equation}
We call the resulting algorithm \textsc{Scale-Free Mirror Descent} with
regularizer $R$.  Generalizing existing regret bound for
\textsc{AdaGrad}~\cite{Duchi-Hazan-Singer-2011} we can upper bound its regret.
Proof is a generalization of the proof
of~\cite{Duchi-Shalev-Shwartz-Singer-Tewari-2010,Duchi-Hazan-Singer-2011} and
it can be found can be found in~\ref{section:mirror-descent-proofs}.
